The Assembly of Black Hole Mass ad Luminosity Functions of High-redshift Quasars\\via Multiple Accretion Episodes

### 2022-09-29 ms.tex
version0929; me added t_Q paragraph; before k's memos

\blue{
Moreover, some individual quasar observations give exceptionally small proximity zone sizes,
indicating short lifetime of their luminous phase $t_{\rm Q} \lesssim 10^4$ yr.
The short quasar lifetime may be due to the young age of quasars ionizing the surrounding IGM \citep[e.g.,][]{2020ApJ...903...60I,2021ApJ...917...38E}.
Our episodic quasar growth model agrees with this argument,
besides alleviates the growth tension of SMBHs by episodic accretion bursts.
In other words, the lifetime of luminous quasar phase is the cumulative time of accreting activity in the current episode.
}

>>>>

\blue{
Moreover, observations on the quasar proximity zone size which traces the ionized IGM bubbles
produce important constraints on the time $t_{\rm Q}$ elapsed with luminous quasar phase
\citep{2007MNRAS.374..493B,2016ApJ...824..133K,2017ApJ...840...24E,2019ApJ...884L..19D}.
Measurements with this method typically point toward a luminous quasar lifetime of $t_{\rm Q} \sim 1$ Myr,
while some individual quasars which are inferred to have exceptionally small proximity zone sizes
with $t_{\rm Q} \lesssim 10^4$ yr,
may be due to the young age of quasars ionizing the surrounding IGM \citep[e.g.,][]{2020ApJ...903...60I,2021ApJ...917...38E}.
Viewed from our episodic BH growth model, the timescale $t_{\rm Q}$ corresponds to the current duration of quasar activity,
thus not necessary the entire quasar lifetime with accretion.
Therefore, our model implies that the difference of the small v.s. normal proximity zone sizes just originates from the different stages they are observed.
% Our episodic quasar growth model agrees with this argument,
% besides alleviates the growth tension of SMBHs by episodic accretion bursts.
% In other words, the lifetime of luminous quasar phase is the cumulative time of accreting activity in the current episode.
On the other hand, transverse proximity effect probes a longer timescale ($\sim 10-100$ Myr) light curve from quasars through the ionizing light-echo in the IGM
\citep{2004ApJ...612..706A,2008ApJ...674..660V,2019ApJ...882..165S,2022MNRAS.516..582K}.
In our episodic BH accretion model, the time duration of accretion activity typically lasts for $\tau\sim 20$ Myr,
and we predict uniform distributions of luminous quasars with lifetimes within this timescale.
Besides, there is a non-negligible fraction $f_{2 \tau}$ of actively accreting quasars to have another super-Eddington in the previous episode,
bearing light-echoes with timescales longer than $\tau$ but sensitive to the transverse proximity effect measurements \citep[see][]{2022MNRAS.516..582K}.
We estimate it to be $f_{2 \tau}\simeq$ 0.09, 0.12, and 0.17,
for massive BH sub-samples with $M_\bullet>10^7$, $10^8$ and $10^9~\Msun$ at $z=$ 6, respectively.
Investigations on the quasar light curves can set strong constraints on the model prescription and improve our understanding on the BH growth histories through luminous quasar phases.
}
